---
title: "draft"
output: html_document
---

```{r}
library(dplyr)
library(bnlearn)
```

## Draft - simulations

### Objectives:

- Generative models:

- S1D: Multiple models with various missingness mechanisms, discrete variables
- S2M: Mixed model, realistic, various missingness mechanisms

- For each model:

- Generate Dtrain and Dtest using theta and phi vectors:
- theta: variables parameters
- phi: missing indicators parameters
- For every algorithm:
- train the algorithm on Dtrain
- predict on Dtest
- measure performance metrics

## Data generation

```{r}
# Generate the DAGs
generationModelList = list("S1M1" = list(dag = model2network("[X1][Y|X1][M1]")),
                           "S1M2" = list(dag = model2network("[X1][X2][Y|X1:X2][M1|X2]")),
                           "S1M3" = list(dag = model2network("[X1][X3][X2|X1:X3][M1|X3][Y|X1:X2]")),
                           "S1M4" = list(dag = model2network("[X1][Y|X1][M1|X1][X2|Y]")),
                           "S1M5" = list(dag = model2network("[X1][X2][Y|X1:X2][M1|Y]")))
```

```{r}
params = list(S1M1 = list(theta = list(X1 = .4,
                                       Y = c(.2, .5)),
                          phi = list(M1 = .4),
                          labels = list(theta = c("TR","FA"),
                                        phi = c("MISS","OBS"))),
              S1M2 = list(theta = list(X1 = .4,
                                       X2 = .4,
                                       Y = c(.2, .5, .3, .7)),
                          phi = list(M1 = c(.4, .2)),
                          labels = list(theta = c("TR","FA"),
                                        phi = c("MISS","OBS"))))
```

```{r}
# feed the parameters for S1

feedS1M1 = function(dag, params){
  theta = params$theta
  phi = params$phi
  labels = params$labels
  
  cptX1 = matrix(c(theta$X1, 1-theta$X1),
                 ncol = 2,
                 dimnames = list(NULL,
                                 c(labels$theta[1:2])))
  
  cptM1 = matrix(c(phi$M1, 1-phi$M1),
                 ncol = 2,
                 dimnames = list(NULL,
                                 c(labels$phi[1:2])))
  
  cptY = c(theta$Y[1], 1-theta$Y[1],
           theta$Y[2], 1-theta$Y[2])
  
  dim(cptY) = c(2, 2)
  dimnames(cptY) = list("Y" = labels$theta,
                        "X1" =  labels$theta)
  
  model = custom.fit(dag,
                     dist = list(X1 = cptX1,
                                 M1 = cptM1,
                                 Y = cptY))
  return(list(dag = dag,
              model = model,
              params = params))
}


generationModelList$S1M1 = feedS1M1(generationModelList$S1M1$dag,
                                    params$S1M1)

generationModelList$S1M1
```

```{r}
feedS1M2 = function(dag, params){
  theta = params$theta
  phi = params$phi
  labels = params$labels
  
  cptX1 = matrix(c(theta$X1, 1-theta$X1),
                 ncol = 2,
                 dimnames = list(NULL,
                                 c(labels$theta[1:2])))
  
  cptX2 = matrix(c(theta$X2, 1-theta$X2),
                 ncol = 2,
                 dimnames = list(NULL,
                                 c(labels$theta[1:2])))
  
  cptY = c(theta$Y[1], 1-theta$Y[1],
           theta$Y[2], 1-theta$Y[2],
           theta$Y[3], 1-theta$Y[3],
           theta$Y[4], 1-theta$Y[4])
  
  dim(cptY) = c(2, 2, 2)
  dimnames(cptY) = list("Y" = labels$theta,
                        "X1" =  labels$theta,
                        "X2" = labels$theta)
  
  cptM1 = c(phi$M1[1], 1-phi$M1[1],
            phi$M1[2], 1-phi$M1[2])
  
  dim(cptM1) = c(2, 2)
  dimnames(cptM1) = list("M1" = labels$phi,
                         "X2" =  labels$theta)
  
  model = custom.fit(dag,
                     dist = list(X1 = cptX1,
                                 X2 = cptX2,
                                 M1 = cptM1,
                                 Y = cptY))
  return(list(dag = dag,
              model = model,
              params = params))
}

generationModelList$S1M2 = feedS1M2(generationModelList$S1M2$dag,
                                    params$S1M2)

generationModelList$S1M2
```

## Todo

- define functions feedS1M3, feedS1M4, feedS1M5
- develop algorithm to:
  - draw random theta
  - for every draw, generate a table of random sample + values of theta and phi
- transfer data to python
- in python:
  - train
  - test
  - measure


